Raft Distributed Consensus Algorithm over WebRTC (Web Real-Time Communication)

### 2015-09-12 research_class/paper.tex
NOT SURE: is this right?
If this is right, I think it's clearer. If it's wrong, then I'm
misunderstanding/misguessing. You may or may not want to consider clarifying
somehow for the other dunderheads like me, who will read this and possibly be
confused.

Each node of the Raft cluster maintains an ordinally increasing
current term value. When a Raft follower node does not receive
a heartbeat from a leader within a random election timeout period, it
transitions to candidate state, votes for itself, increases its
current term value by one and sends a requestVote RPC (with the
new term) to all the other nodes in the cluster. When a node receives
a requestVote RPC with a term that is greater than its own it will
become a follower (if not already), update its term to the new term,
and send a RPC response back that indicates a vote for that candidate.
However, a node may only vote for one candidate in a given term. If
a candidate receives votes from more than half of the cluster, then it
immediately becomes a leader and sends out a appendEntries RPC to
confirm leadership and reset the election timers on all the other
nodes \cite[Section~3.4]{raft_thesis:ongaro14}.

>>>>

Each node of the Raft cluster maintains an ordinally increasing
current term value. When a Raft follower node does not receive
a heartbeat from a leader within a locally randomized election timeout period, it
transitions to candidate state, votes for itself, increases its
current term value by one and sends a requestVote RPC (with the
new term) to all the other nodes in the cluster. When a node receives
a requestVote RPC with a term that is greater than its own it will
become a follower (if not already), update its term to the new term,
and send a RPC response back that indicates a vote for that candidate.
However, a node may only vote for one candidate in a given term. If
a candidate receives votes from more than half of the cluster, then it
immediately becomes a leader and sends out a appendEntries RPC to
confirm leadership and reset the election timers on all the other
nodes \cite[Section~3.4]{raft_thesis:ongaro14}.
